Online Laterality Battery Pre-Processing - short version

### 2020-06-11 battery-preprocessing_v5_DB.Rmd
osf links updated

  # new data
  wanted <- c("Trial","subject", "Correct", "RT", "ANSWER","Response","word","Left_image","Right_image") # select wanted columns
  RDT_dat2 <- procdata(origfile,wanted,task,disp) #Here we reuse the procdata function that we developed for processing Chimeric faces data - just does some generic processing

@@

  thisdat <- thisdat[thisdat$outlier==0,] #remove outliers
  aggdata <- aggregate(thisdat$RT,by=list(thisdat$side,thisdat$item,thisdat$subject),
                       FUN=mean,na.rm=TRUE)
  colnames(aggdata)<-c('side','item','subject','RT')
  mysubs<-unique(aggdata$subject)
  if(d==1){
  pairedt <- data.frame(matrix(NA,nrow=length(mysubs),ncol=5))
  colnames(pairedt) <- c('subject','t1','p1','t2','p2')
  }
  nsubs<-length(mysubs)
  for (i in 1:nsubs){
    myt<-NA
    myp<-NA
    thisdat <- aggdata[aggdata$subject==mysubs[i],]
    pairedt$subject[i]<- mysubs[i]
    #check there are data for both left and right on all items
    checkdat <-table(thisdat$item)
    w<-which(checkdat<2)
    if(length(w)==0){
      t<-t.test(thisdat$RT[thisdat$side=='left'],thisdat$RT[thisdat$side=='right'],paired=T)
      myt<-t$statistic
      myp<-t$p.value
    }
    if(d==1){
      pairedt$t1[i] <- myt
      pairedt$p1[i] <-myp
    }
    if(d==2){
      pairedt$t2[i] <-myt
      pairedt$p2[i] <-myp
    }
  }
}

# add t score to the data
t_dat <- select(pairedt, -3, -5)
# merge to allsum for analysis
allsum <- merge(allsum, t_dat)

>>>>

  # new data
  wanted <- c("Trial","subject", "Participant.Public.ID", "Correct", "RT", "ANSWER","Response","word","Left_image","Right_image") # select wanted columns
  RDT_dat2 <- procdata(origfile,wanted,task,disp) #Here we reuse the procdata function that we developed for processing Chimeric faces data - just does some generic processing

@@

  thisdat <- thisdat[thisdat$outlier==0,] #remove outliers
  aggdata <- aggregate(thisdat$RT,by=list(thisdat$side,thisdat$item,thisdat$Participant.Public.ID),
                       FUN=mean,na.rm=TRUE)
  aggdata$subject <- aggdata$Participant.Public.ID
  colnames(aggdata)<-c('side','item','subject','RT')
  mysubs<-unique(aggdata$subject)
  if(d==1){
  pairedt <- data.frame(matrix(NA,nrow=length(mysubs),ncol=5))
  colnames(pairedt) <- c('subject','t1','p1','t2','p2')
  }
  nsubs<-length(mysubs)
  for (i in 1:nsubs){
    myt<-NA
    myp<-NA
    thisdat <- aggdata[aggdata$subject==mysubs[i],]
    pairedt$subject[i]<- mysubs[i]
    #check there are data for both left and right on all items
    checkdat <-table(thisdat$item)
    w<-which(checkdat<2)
    if(length(w)==0){
      t<-t.test(thisdat$RT[thisdat$side=='left'],thisdat$RT[thisdat$side=='right'],paired=T)
      myt<-t$statistic
      myp<-t$p.value
    }
    if(d==1){
      pairedt$t1[i] <- myt
      pairedt$p1[i] <-myp
    }
    if(d==2){
      pairedt$t2[i] <-myt
      pairedt$p2[i] <-myp
    }
  }
}

# add t score to the data
t_dat <- select(pairedt, -3, -5)
t_dat <- na.omit(t_dat)
# merge to allsum for analysis
allsum <- merge(allsum, t_dat, by.x = "origID", by.y = "subject", all.x=T)
